Recent advances of Malaria parasites detection systems based on mathematical morphology techniques

### 2017-11-17 Paper.tex
Added table comparisons

	The paper in \cite{Kareem2012_1} illustrates a morphological approach for blood cell identification and uses the image features such as intensity, histogram, relative size and geometry for further analysis. Before the identification of blood cells, the authors  propose a novel morphological filtering based on the size of RBC for platelets and/or artifacts elimination. A dilation is performed by a concentric ring structuring element and erosion by disk shaped structuring element. The radius of the structuring element depends on the radius of the RBC, so that all the components smaller than the RBCs are removed.

@@

@@

	The authors in \cite{Arco2015} worked on thick blood films and proposed a method that uses an adaptive thresholding based scheme, which also allows an effective classification of pixels. This means that the election of whether a pixel belongs to the background or to the signal (parasites and white blood cells) is only established by the pixels around it, that is its neighbourhood. Then, morphological methods are applied to evaluate the area of connected components, labelling those belonging to parasites and counting their number. The following strategy has been used:
	\begin{enumerate}
		\item an algorithm based on run-length encoding has been used for analysing the connected components of the binary masks obtained in segmentation phase;
		\item preliminary tagging, keeping the label equivalences or connected regions with different labels in a table of local matches. Resolution of the equivalences is, then, performed;
		\item measurements on the remaining connected components: WBCs and MP region areas are checked and WBCs connected components are removed with a closing operation.
	\end{enumerate}
	%
	Also in the method proposed in \cite{Somasekar2017} the segmentation of the infected parasites is based on thresholding. The segmentation is achieved in two stages by maximizing between-class variance of an original image and consequently by an iterative threshold selection from a stage-one threshold image with suitable stopping criteria. The segmented results are post processed to improve the accuracy of the detection of malaria
	parasites by morphological operators (erosion and closing).

@@

	To conlude many systems for computer aided diagnosis of malaria disease made use of mathematical operatations in order to smoothen the boundary of the regions obtained from the segmentation process, like in \cite{Dave2017}.

@@

>>>>

	The paper in \cite{Kareem2012} illustrates a morphological approach for blood cell identification and uses the image features such as intensity, histogram, relative size and geometry for further analysis. Before the identification of blood cells, the authors  propose a novel morphological filtering based on the size of RBC for platelets and/or artifacts elimination. A dilation is performed by a concentric ring structuring element and erosion by disk shaped structuring element. The radius of the structuring element depends on the radius of the RBC, so that all the components smaller than the RBCs are removed.

@@

	Dave et al. in \cite{Dave2017} image segmentation is performed using histogram based adaptive thresholding followed by mathematical morphological operations (erosion and dilatioon). The detection of infected RBC is based on a unsupervised learning technique.

@@

	The authors in \cite{Arco2014} worked on thick blood films and proposed a method that uses an adaptive thresholding based scheme, which also allows an effective classification of pixels. This means that the election of whether a pixel belongs to the background or to the signal (parasites and white blood cells) is only established by the pixels around it, that is its neighbourhood. Then, morphological methods are applied to evaluate the area of connected components, labelling those belonging to parasites and counting their number. The following strategy has been used:
	\begin{enumerate}
		\item an algorithm based on run-length encoding has been used for analysing the connected components of the binary masks obtained in segmentation phase;
		\item preliminary tagging, keeping the label equivalences or connected regions with different labels in a table of local matches. Resolution of the equivalences is, then, performed;
		\item measurements on the remaining connected components: WBCs and MP region areas are checked and WBCs connected components are removed with a closing operation.
	\end{enumerate}
	%
	Also in the method proposed in \cite{Somasekar2017} the segmentation of the infected parasites is based on thresholding. The segmentation is achieved in two stages by maximizing between-class variance of an original image and consequently by an iterative threshold selection from a stage-one threshold image with suitable stopping criteria. The segmented results are post processed to improve the accuracy of the detection of malaria
	parasites by morphological operators (erosion and closing).

@@

	To conlude many systems for computer aided diagnosis of malaria disease made use of mathematical operatations in order to smoothen the boundary of the regions obtained from the segmentation process.

@@

	\input{Table_sum.tex}
